Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-10-29 paper/main.tex
make rescaling of parameters more clear

where $\lambda$ a damping constant and the mass was set to $1$ to simplify the model.

>>>>

where $\lambda$ a damping constant.
The equations have been rescaled by dividing with the mass, thus effectively eliminating this
parameter and simplifying the model.
All involved parameters and their units can be viewed in Table~\ref{table:list-of-parameters}.
